A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2020-04-10 paper/paper-revision.Rnw
Finish polishing intro

However, a number of footwear studies (such as those by \citep{parent_sandy_significance_nodate} and \citep{benedict_geographical_2014}) have demonstrated that even a couple hundred shoe prints constitute an unweildy amount of data that require a large amount of time and effort to process and analyze. Thus, in parallel with the development of the aforementioned scanner, it is necessary to develop a way to process large amounts of data automatically. The primary focus of this paper is the development of one such method for large-scale automatic data processing, where "data processing" refers to assessing the similarity of the shoe tread patterns in the collected data.

Although footwear impressions are more commonly used in practice for footwear analysis than outsole images, our early prototypes of a footwear scanner have suggested that cameras are more robust than pressure scanners for placement in public locations, which may experience inclement weather or other non-controlled conditions. Thus, we are working to develop a scanner that uses cameras to take pictures of shoe outsoles, much like images that are currently found on the websites of online shoe retailers \autoref{fig:prototype-scanner}. Although the images from the scanner are more degraded in some ways than images found from online retailers, the fundamental requirements to analyze such data would be similar. Therefore, \fix{we move forward by considering how to assess similarity of tread patterns in images of outsoles, in particular.} More specifically, this assessment is done by identifying a set of relevant features and using image analysis methods to detect the presence or absence of the features in each image, and then defining similarity measures based on those features to determine how many shoes have a tread pattern similar to the pattern of interest.

@@

@@

% From original intro:
In this paper, we discuss an alternate approach that uses an additional model layer to transfer the feature vector output into a vector of probabilities representing the detection of geometric elements in shoe tread images. Working within the feature space used by forensic examiners allows us to augment human-identified features with model output, assessing similarity of different shoe images on a feature set that is explicitly relevant to the domain. \fix{Ultimately, we can use the output probabilities to quantify similarity between tread patterns for the ultimate goal of calculating random match probability for a given tread pattern.}

\mt{subsection: motivation (w/ pics of scanner)}

>>>>

However, a number of footwear studies (such as those by \citep{parent_sandy_significance_nodate} and \citep{benedict_geographical_2014}) have demonstrated that even a couple hundred shoe prints constitute an unweildy amount of data that require a large amount of time and effort to process and analyze. Thus, in parallel with the development of the aforementioned scanner, it is necessary to develop a way to process large amounts of data automatically. The primary focus of this paper is the development of one such method for large-scale automatic data processing.

Although footwear impressions are more commonly used in practice for footwear analysis than outsole images, our early prototypes of a footwear scanner have suggested that cameras are more robust than pressure scanners for placement in public locations, which may experience inclement weather or other non-controlled conditions. Thus, we are working to develop a scanner that uses cameras to take pictures of shoe outsoles, much like images that are currently found on the websites of online shoe retailers \autoref{fig:prototype-scanner}. Despite the fact that images from the scanner would be more degraded in some ways than images found from online retailers, the fundamental requirements to analyze such data would be similar. Thus, retailer images provide a reasonable basis for the development of a method to assess similarity in tread images. More specifically, this assessment is done by identifying a set of relevant features and using image analysis methods to detect the presence or absence of the features in each image, and then defining similarity measures based on those features to determine how many shoes have a tread pattern similar to the pattern of interest.

@@

\subsection{Image Analysis}

@@

% From original intro:
In this paper, we discuss an alternate approach that uses an additional model layer to transfer the feature vector output into a vector of probabilities representing the detection of geometric elements in shoe tread images. Working within the feature space used by forensic examiners allows us to augment human-identified features with model output, assessing similarity of different shoe images on a feature set that is explicitly relevant to the domain. \fix{Ultimately, the output probabilities can be used to quantify similarity between tread patterns for the ultimate goal of calculating random match probability for a given tread pattern.}
